Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-24 manual/projectrapport.tex
GXVAD XAXFX FXVAD FGAGA GDGAG AVAGX VDGGF DVXAV AXFXF VDDDV VFDVA GAGGG DDFGD DGVDA VVFVV VGAVX

\chapter{Planning}
\section{Parallel}
\begin {itemize}
\item GVT integration : week 0-1, Ben and Tim
\item Conservative : week 2-3 , Ben and Tim
\end {itemize}
\section{General}
\begin {itemize}
\item Dynamic Structured : week 1-3 Stijn
\item DevStone and examples : week 0-2 Matthijs and Pieter
\item Serialization : week 0 Pieter
\item Simulation control : week 1-3 Matthijs and Pieter  
\item Tracers : week 0 Stijn
\item Benchmarking PyPDevs Adevs : week 3 Matthijs and Pieter
\end {itemize}
\section{Optimization}
Week 4 general review.

@@

\chapter{Performance Analysis}
Whenever we made big design/architecture decisions, we first wrote some prototyping testcode to prove the viability (e.g. Network, Tracing, Logger).
\section{First comparison}
We use perf to get statistically sound benchmarks. The command run was :
\lstinline!$perf stat -r {rounds} {command}!\\

\subsection{Classic}
An endtime of 3.6e6 was set, and both examples run against each other.
\lstinputlisting[]{pycla.txt}
The following shows a recording of the C++ implementation of the same example.\\
\lstinputlisting[]{cpcla.txt}
\subsubsection{Conclusion}
The C++ port is approximately 12.906 times faster.

\subsection{Dynamic structured}
An end-time of 3.6e6 was set, and both examples run against each other.
\lstinputlisting[]{pydyn.txt}
The following shows a recording of the C++ implementation of the same example.\\
\lstinputlisting[]{cpdyn.txt}
\subsubsection{Conclusion}
This result is still warped due to the startup/shutdown time of GTEST, but allready the C++ port is roughly 7.05 times faster, only page faults and migrations are worse (but being worked on).
\subsection{Parallel}
With GVT not yet active, an endtime of 3.6e6 was used (as before).\lstinputlisting[]{pypar.txt}\
The following shows a recording of the C++ implementation of the same example.\\
\lstinputlisting[]{cppar.txt}
\subsubsection{Conclusion}
The C++ port is approximately 19.6 times faster.

>>>>

@@

\chapter{Logger analysis}
